Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-04-04 document/ms.tex
description of completeness model

\dfmtodo{%
Describe Erik's data products and our model of the completeness in boxes
extended artificially beyond the original range.
Also describe the re-sampling procedure for the candidate parameters.
}

>>>>

Erik Petigura and collaborators (\citealt{petigura-a,petigura}) heroically
determined the empirical end-to-end completeness of their transit search
pipeline by injecting synthetic signals of known period and radius into the
raw aperture photometry and testing recovery rates.
They also published a catalog of XXX small planet candidates around G type
stars; YYY of them previously unknown.
Given the unprecedented quality of the completeness characterization, we will
focus on this dataset in this \paper.

We use all the injected samples from \citet{petigura} to compute the mean
(marginalized) detection efficiency in bins of $\ln\period$ and $\ln\radius$.
In each bin, this efficiency is simply the fraction of recovered injections.
For the purposes of this \paper, we will neglect the uncertainties introduced
by the fact that this estimate is being made with a finite number of samples.

The largest injected radius is $16\,R_\oplus$ but, because of the measurement
uncertainties on the radii, it will be necessary for us to model the
distribution to larger radii.
To do this, we approximate the survey completeness for $\radius > 16\,R\oplus$
as 1.

\dfmtodo{Hopefully Erik will send us MCMC samples. If not, describe the
re-sampling procedure that we used. Either way, we'll need to re-sample under
the completeness probability for the purposes of the importance sampling.}
